Learning how to act: making good decisions with machine learning

### 2017-07-01 thesis/offcuts.tex
draft of section on adversarial bandits done

@@

>>>>

\section*{Causality and marketing}
\begin{itemize}
\item If your sales are entirely online, can you attribute all sales to marketing because; start with 0 sales. Spend some dollars on marketing, which leads to customers. Additional sales can occur because of customer experience, word of mouth or new advertising, but regardless these additional sales are a consequence of the advertising spend at time 0. (what about natural search)? 
\item Do we have any idea how people found out about us (when they purchase our brands?), ie from search, from a friend, etc
\item The previous arguament doesn't apply when there are physical stores - since people may find out about the product without any advertising in that case. 
\item Does buying visits through paid search increase the ranking one acheives in natural search. 
\item would be interesting to analyse natural search position as a function of market share. 
\end{itemize}

@@

\todo{connect bandit regret to early stopping of experiment problem}
The problem of when to stop an experiment early can also be phrased as a bandit problem and analysed with the same techniques. XXX et al showed that if use an experimental setup with early stopping, the regret you obtain will be at least twice that you could have achieved had you made each decision sequentially using a bandit approach. Of course this neglect any costs that might be associated with the complexity in implementation of the two approaches.

The bandit learning algorithm is sometimes compared to the standard supervised learning in terms of the feedback recieved. One way of viewing the standard supervised learning setting is that the label for each instance corresponds to the correct or optimal choice for that setting. However, this does not have to be the case. In the bandit setting the algorithm observes only the reward for the selected action. How are standard supervised learning problems translated to bandit problems for testing algorithms? (is it contextual bandit problems?)

Bandit algorithms that require the horizon $T$ to be known in advance are refered to as \emph{fixed horizon} algorithms, as opposed to \emph{anytime} algorithms that do not rely on knowing the horizon. A fixed horizon algorithm may be converted to an anytime algorithm via the so called "doubling trick" \citep{}. The algorithm starts with some fixed horizon and increases it at a fixed rate everytime the current horizon is reached until the problem terminates. \todo{what can be said about the optimality of this?}

In the classical multi-armed bandit problem, the rewards for each arm are sampled stochastically from a fixed (but unknown) distribution. There is a large body of work analysing a more general formulation of the bandit problem that relaxes this stochastic assumption.

This lower bound says that for any algorithm for the k-armed bandit problem, there exists a set of reward distributions such that the expected is $\bigomega{\sqrt{kT}}$.

The expectation is with respect the random sequence of actions.

### 2017-07-01 thesis/thesis_map.tex
draft of section on adversarial bandits done

\newcommand{\KL}{\operatorname{KL}}
\newcommand{\simpleregret}{R_T}
\newcommand{\Pij}[1]{\operatorname{P}_{ij}\!\left\{#1\right\}}
\newcommand{\Pkl}[1]{\operatorname{P}_{kl}\!\left\{#1\right\}}
\newcommand{\Q}[1]{\operatorname{Q}\left(#1\right)}
\newcommand{\EE}{\mathbb E}
\newcommand{\EEa}{\EE_a}
\newcommand{\Pns}[2]{\operatorname{P}_{#1}\left\{#2\right\}}
\newcommand{\Pn}[2]{\operatorname{P}\left\{#2|#1\right\}}
\newcommand{\actions}{\mathcal{A}}
\newcommand{\calA}{\mathcal A}
\newcommand{\etc}{\textit{etc}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\calP}{\mathcal P}
\newcommand{\x}{\boldsymbol{x}}
\newcommand{\Ps}{\operatorname{P}}
\newcommand{\R}{\mathbb R}
\newcommand{\Pri}[1]{\operatorname{P}_i\left\{#1\right\}}
\newcommand{\Prz}[1]{\operatorname{P}_0\left\{#1\right\}}
\newcommand{\indep}[1]{\mathcal{I}\left(#1\right)}
\newcommand{\vb}[1]{\boldsymbol{#1}}
\newcommand{\card}[1]{\left\vert{#1}\right\vert}
\newcommand{\actionspace}{\mathcal{A}}

@@

\renewcommand{\P}[1]{\operatorname{P}\left(#1\right)}
\newcommand{\cf}[2]{{#1}^{#2}}
\newcommand{\bernoulli}{\operatorname{Bernoulli}}
\newcommand{\dirac}{\operatorname{Dirac}}
\newcommand{\parents}[1]{\operatorname{\mathcal{P}a}_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\regret}{\bar{R}_{T}} %psuedo-regret
\newcommand{\expectedregret}{\mathbb{E}R_{T}} % expected regret
\newcommand{\rawregret}{R_{T}} % plain regret 
\newcommand{\quotes}[1]{``#1''}

@@

\chapter*{Todo}
\begin{enumerate}
\item Add something about Granger causality - does this belong in chapter 2 or chapter 3?
\end{enumerate}

@@

Both the rewards and the actions selected by the algorithm are random variables. The majority of work in the bandit liturature focuses on analysing and optimising some form of the expected regret, however there has been some work that also considers the concentration of the regret \citep{Audibert2007}. The expectation of the regret, as defined by equation \ref{eqn:raw_regret}, is refered to as the pseudo-regret \citep{Bubeck2012} and is given by equation \ref{eqn:pseudo_regret}. A stochastic bandit algorithm is learning if it obtains psuedo-regret that is sub-linear in $T$.

@@

\subsection{Approaches, Regret bounds and results}

The adaptive nature of multi-armed bandit algorithms complicates the design and analyse of estimators. The action selected by an algorithm at a given timestep can depend on the history of previous actions and rewards. As a result, the probability that each action is selected evolves over time, the actions are not sampled i.i.d from a fixed distribution and the number of times each action is selected is a random variable. The expectation and variance guarentees of standard estimators do not hold in this setting, see figure \ref{fig:early_stopping} for a concrete example. This makes it very difficult to  obtain an analytical expression for the expected regret for a given algorithm and problem. Instead, we focus on computing upper and lower bounds on the regret.

@@

Talk about problem dependent and worst case bounds

Lay out what they are for the stochastic bandit setting.

\begin{itemize}
\item problem dependent versus worst-case bounds
\item upper and lower bounds
\end{itemize}
Here we can talk about the different kinds of bounds that are possible to achieve and what has been done so far (for stochastic k-armed bandits)

The lower bound on the worst case regret for any algorithm (stochastic or adversarial) for the K-armed bandit problem is  $\bigomega{\sqrt{TK}}$ \cite{Auer1995}.

A key algorithm for stochastic bandits, with tractable analysis and strong performance guarantees, is the UCB algorithm \cite{Auer2002}. They key to this algorithm is that it keeps track of an upper confidence bound (hence UCB) on the expected reward for each arm and selects the arm with the highest one. This balances exploration and exploitation as an arm with a high upper confidence bound must have either a high expected reward or large uncertainty on the expected reward. Assume for rotational simplicity that $\mu_1 > \mu_2 > ... > \mu_K$, such that $\mu^* = \mu_1$, and let $\Delta_i = \mu_i - \mu^*$ be the sub-optimal for each arm. The (problem dependent) regret for UCB is bounded by:

\eqn {
R^{ucb}(T) \in \bigo{\sum_{i=2}^K \frac{1}{\Delta_i}\log(T)}
}

This bound blows up as differences $\Delta_i \rightarrow 0$, however the regret itself does not - since although we may not be able to distinguish arms with very small $\Delta_i$ from the optimal arm, we also do not lose much by selecting them. In the worst case, $R^{ucb}(T) = \bigo{\sqrt{TK\log(T)}}$ \cite{Bubeck2012}. Subtle modifications to the UCB algorithm can eliminate the logarithmic term in this worst case regret bound. This yields $R^{ucb}(T) = \bigo{\sqrt{TK}}$ and closes the gap with the worst case lower bound \cite{Audibert2009,Lattimore2015}, whilst retaining a good problem dependent bound of the form achieved by UCB \cite{Lattimore2015}.

One key principle that has motivated the design of a number \todo{ask Tor are there actually others aside from UCB?} of key bandit algorithms is the idea of \emph{optimism in the face of uncertainty}. An algorithm is trying to simultaneously obtain large rewards and extract as much information as possible. If an action has a high upper bound on the possible reward then either the expected reward must be high or the algorithm must be very uncertain about it. Choosing it should yield either a good reward or useful information. This is the key idea behind the UCB algorithm \citep{xxx}. The remaining complexity lies in optimising how we compute confidence intervals to trade of exploration and exploitation as the game proceeds. Subtle variations in how the confidence intervals are defined lead to a number of algorithms, which are optimised to slightly different settings. SETTINGS NOT QUITE RIGHT WORD. \citep{xxx}.

The bandit learning algorithm is sometimes compared to the standard supervised learning in terms of the feedback recieved. One way of viewing the standard supervised learning setting is that the label for each instance corresponds to the correct or optimal choice for that setting. However, this does not have to be the case. In the bandit setting the algorithm observes only the reward for the selected action. How are standard supervised learning problems translated to bandit problems for testing algorithms? (is it contextual bandit problems?)

Bandit algorithms that require the horizon $T$ to be known in advance are refered to as \emph{fixed horizon} algorithms, as opposed to \emph{anytime} algorithms that do not rely on knowing the horizon. A fixed horizon algorithm may be converted to an anytime algorithm via the so called "doubling trick" \citep{}. The algorithm starts with some fixed horizon and increases it at a fixed rate everytime the current horizon is reached until the problem terminates. \todo{what can be said about the optimality of this?}

Another problem that has attracted a lot of recent attention \cite{Bubeck2009,Audibert2010,Gabillon2012,Karnin2013} within the multi-armed bandit framework is \textit{pure exploration} or \textit{best arm identification}. In this setting, the horizon $T$ represents a fixed budget for exploration after which the algorithm outputs a single best arm $i$. The performance of the algorithm is measured by the simple regret; the expected difference between the mean reward of the (truly) optimal arm and the mean reward of the arm selected by the algorithm.

\vspace{0.5cm}
\begin{definition}[Simple Regret]
\eqn{
\label{eqn:simple_regret}
\mu_{i^*} - \E{\mu_{\hat i^*}}.
}
\end{definition}

The best arm identification problem arises naturally in applications where there is a testing or evaluation phase, during which regret is not incurred, followed by a commercialisation or exploitation phase. For example, many strategies might be assessed via simulation prior to one being selected and deployed. The simple regret for a K-armed bandit is lower bounded by $\bigo{\sqrt{K/T}}$ \cite{Bubeck2009}.

\todo{connect bandit regret to early stopping of experiment problem}
The problem of when to stop an experiment early can also be phrased as a bandit problem and analysed with the same techniques. XXX et al showed that if use an experimental setup with early stopping, the regret you obtain will be at least twice that you could have achieved had you made each decision sequentially using a bandit approach. Of course this neglect any costs that might be associated with the complexity in implementation of the two approaches.

\subsection{Key related settings}

\subsubsection{Adversarial Bandits}
In the classical multi-armed bandit problem, the rewards for each arm are sampled stochastically from a fixed (but unknown) distribution. There is a large body of work analysing a more general formulation of the bandit problem that relaxes this stochastic assumption.

Adversarial bandits are an alternate, widely studied, setting that relaxes the assumption that rewards are generated stochastically. Instead, simultaneously with the learner selecting an action $I_t$, a potentially malicious adversary selects the reward vector $\boldsymbol{g}_t$. As in the stochastic setting, the learner then receives reward $g_{I_t,t}$. The seminal algorithm for adversarial bandits is Exp-3, which, like UCB, obtains regret $\bigo{\sqrt{TK\log(T)}}$ regret \cite{Auer1995}. Optimal algorithms, with $R(T) = \bigo{\sqrt{TK}}$, have also been demonstrated for the adversarial setting \cite{Audibert2009}.

\paragraph*{Definition of the Adversarial bandit problem}
\begin{itemize}
\item Different notation of regret
\item Adversarial bandits are not immune to issues of feedback cycles or drift in the reward distribution because a constancy is implicit in the definition of regret. 
\end{itemize}

\subsubsection{Contextual bandits}
Contextual bandits are a generalisation of multi-armed bandits.

@@

\subsubsection{Markov decision processes}

@@

This is reasonable in settings where we have many similar but independent units or individuals and the goal is to identify which action is optimal (in a given context). However

@@

\section{Questions}
\begin{enumerate}
\item When does the expected regret make sense as the thing we actually would wish to optimise? Is optimising the expected regret any different to optimising the psuedo-regret? Who is the definition of regret down to? Does this definition of regret come from learning with expert advise?
\item Is there a reference for the doubling trick? Is it an automatic way of converting a fixed horizon algorithm to an anytime one?
\item Why is the dependence on the number of arms $K$ in the problem dependent bounds but $\sqrt{K}$ in the worst case bounds?
\item rewards in the multi-armed bandit setting can be sampled from some joint distribution?
\item Is Learning from logged feedback data just covariate shift too?
\item In contextual bandits, does it ever make sense that $Y$ causes $X$? If the reward is some function of the action taken and the context, then the full vector of counterfactual outcomes $Y$ is never instantiated. Are there any implications of this for inference?
\item Why does anything solving a regression problem work in the anti-causal direction - it would seem to break the fundamental underlying assumption of additive noise?
\end{enumerate}

>>>>

\newcommand{\KL}{\operatorname{KL}}

\newcommand{\Pij}[1]{\operatorname{P}_{ij}\!\left\{#1\right\}}
\newcommand{\Pkl}[1]{\operatorname{P}_{kl}\!\left\{#1\right\}}
\newcommand{\Q}[1]{\operatorname{Q}\left(#1\right)}
\newcommand{\EE}{\mathbb E}
\newcommand{\EEa}{\EE_a}
\newcommand{\Pns}[2]{\operatorname{P}_{#1}\left\{#2\right\}}
\newcommand{\Pn}[2]{\operatorname{P}\left\{#2|#1\right\}}
\newcommand{\actions}{\mathcal{A}}
\newcommand{\calA}{\mathcal A}
\newcommand{\etc}{\textit{etc}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\calP}{\mathcal P}
\newcommand{\x}{\boldsymbol{x}}
\newcommand{\Ps}{\operatorname{P}}
\newcommand{\R}{\mathbb R}
\newcommand{\Pri}[1]{\operatorname{P}_i\left\{#1\right\}}
\newcommand{\Prz}[1]{\operatorname{P}_0\left\{#1\right\}}
\newcommand{\indep}[1]{\mathcal{I}\left(#1\right)}
\newcommand{\vb}[1]{\boldsymbol{#1}}
\newcommand{\card}[1]{\left\vert{#1}\right\vert}
\newcommand{\actionspace}{\mathcal{A}}

@@

\renewcommand{\P}[1]{\operatorname{P}\left(#1\right)}
\newcommand{\cf}[2]{{#1}^{#2}}
\newcommand{\bernoulli}{\operatorname{Bernoulli}}
\newcommand{\dirac}{\operatorname{Dirac}}
\newcommand{\parents}[1]{\operatorname{\mathcal{P}a}_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\regret}{\bar{R}_{T}} %psuedo-regret
\newcommand{\expectedregret}{\mathbb{E}R_{T}} % expected regret
\newcommand{\rawregret}{R_{T}} % plain regret
\newcommand{\simpleregret}{R_T}
\newcommand{\quotes}[1]{``#1''}

@@

\chapter*{Todo}
\begin{enumerate}
\item Add something about Granger causality - does this belong in chapter 2 or chapter 3?
\item Sell my PhD as two key contribution. 1) A technical one, the other educational and unifying (accross viewpoints)
\item Add a chapter in 'PhD prose' making some statement about the intersection of prediction and causality. When is a problem causal, what bounds does predictive accuracy give on causal models? To what degree is predictive accuracy a metric on which causal models can be judged? 
\item Benchmark estimation algorithms
\item clarify causal interpretation of dirichlet models
\item Empirical evaluation of bandit algorithms (updated to include latest suggestions). Maybe a proper software benchmarking solution?
\item If comparing bandit performance, it would be interesting to include some that violate the stochastic bandit assumption. For example, if the rewards change slowly over time or jump suddenly a limited number of times, or with some small probability. 
\end{enumerate}

@@

Both the rewards and the actions selected by the algorithm are random variables. The majority of work in the bandit liturature focuses on analysing and optimising some form of the expected regret, however there has been some work that also considers the concentration of the regret \citep{Auer1995,Audibert2007,Audibert2009exploration}. The expectation of the regret, as defined by equation \ref{eqn:raw_regret}, is refered to as the pseudo-regret \citep{Bubeck2012} and is given by equation \ref{eqn:pseudo_regret}. A stochastic bandit algorithm is learning if it obtains psuedo-regret that is sub-linear in $T$.

@@

The regret is invariant to adding a constant to the expected rewards for all actions. However, it still depends on key characteristics of the reward distributions for each action. Bandit algorithms are designed given assumptions about the form of the distributions, such as that they come from a given family (i.e bernoulli bandits, gaussian bandits) or that the rewards are bounded in some range. Given these assumptions, the performance of the algorithm is characterised in two ways; by the \emph{problem dependent regret}, which typically depends on how far each arm is from optimal and by the \emph{worst case regret}, which is the maximum regret over all possible configurations of the reward distributions (for a given horizon $T$ and number of arms $k$).

\todo{consider mentioning Thompson sampling and Bayesian bandits}

\subsection{Stochastic bandits: Approaches and results}

The adaptive nature of multi-armed bandit algorithms complicates the design and analyse of estimators. The action selected by an algorithm at a given timestep can depend on the history of previous actions and rewards. As a result, the probability that each action is selected evolves over time, the actions are not sampled i.i.d from a fixed distribution and the number of times each action is selected is a random variable. The expectation and variance guarentees of standard estimators do not hold in this setting, see figure \ref{fig:early_stopping} for a concrete example. This makes it very difficult to  obtain an analytical expression for the expected regret for a given algorithm and problem. Instead, the focus is on computing bounds on the expected regret.

@@

There are a few key hueristic principles that are used to guide the development of bandit algorithms. The first is \emph{optimism in the face of uncertainty}. Applied to stochastic bandits, the optimism in the face of uncertainty princple suggests computing a plausible upper-bound for the expected reward of each arm, and selecting the arm with the highest upper bound. The optimism principle encourages exploitation and exploration because a high upper bound on the expected reward for an action implies either the expected reward or the uncertainty about the reward for that action is high. Thus selecting it yields either a good reward or useful information.

\citet{Lai1985} leveraged the optimism in the face of uncertainty principle to develop an algorithm for specific families of reward distributions, including the expontial family. They showed that, for a given bandit problem, the pseudo-regret increased with $\bigo{log(T)}$ asymptopically and proved this is asymptopically efficient. However, their algorithm is complex and memory intensive to compute as, at each timestep, it relies on the entire sequence of rewards for each arm. \citet{Agrawal1995} developed a simpler algorithm that computed upper bounds based only on the mean of previous samples for each arm, whist retaining the logarithmic dependence on $T$. Finally, \citet{Auer2002} developed the UCB-1 algorithm, see algorithm \ref{alg:ucb-1}, which requires only that the reward distributions are bounded, and proved finite-time regret bounds. We now assume the rewards are bounded in $[0,1]$. The algorithm and regret bounds can be generalised to subgaussian reward distributions, see \citet{Bubeck2012}.

\begin{algorithm}[H]
\caption{UCB-1}\label{alg:ucb-1}
\begin{algorithmic}[1]
\STATE {\bf Input:} horizon $T$.
\STATE Play each arm once. 
\FOR{$t \in 1,\ldots,T$}
\STATE Count the number of times each arm has been selected previously $n_{t,i} = \sum_{s=1}^{t-1} \ind{a_s = i}$
\STATE Calculate the mean reward for each arm $\hat{\mu}_{t,i} = \frac{1}{n_{t,i}} \sum_{s=1}^{t-1}\ind{a_s = i}Y_t$
\STATE Select arm $a_t \in \argmax_{i = \set{1,...,k}}\left(\hat{\mu}_{t,i}+\sqrt{\frac{2 \log{t}}{n_{t,i}}}\right)$
\ENDFOR
\end{algorithmic}
\end{algorithm}

Let $\Delta_i = \mu_i - \mu^*$ be degree to which each arm is sub-optimal. The problem dependent psuedo-regret for UCB-1 is bounded by equation \ref{eqn:ucb_problem_dependent_regret} \citep{Bubeck2012},

\eqn {
\label{eqn:ucb_problem_dependent_regret}
\regret \leq & \sum_{i:\Delta_i > 0}\left(\frac{8\log(T)}{\Delta_i}+2 \right)
}

Somewhat unintuitively, the regret increases as the value of the arms gets closer together. This is because it becomes harder for the algorithm to identify the optimal arm. As the differences $\Delta_i \rightarrow 0$, the regret bound in \ref{eqn:ucb_problem_dependent_regret} blows up, however the regret itself does not - since although we may not be able to distinguish arms with very small $\Delta_i$ from the optimal arm, we also do not lose much by selecting them. The worst case occurs if all arms have the same expected reward $\mu$ except for the optimal arm which has reward $\mu^*=\mu+\Delta$, where $\Delta$ is just too small for the algorithm to learn to identify which arm is optimal given the horizon $T$. The regret cannot exceed what would be obtained by selecting the a sub-optimal arm in every timestep, $T\Delta$, so the worst case regret is bounded by the minimum of equation \ref{eqn:ucb_problem_dependent_regret} and $T\Delta$ which ia maximised when they are equal, see figure \ref{fig:ucb_regret_vs_delta}. By solving this equality for $\Delta$ one can show the worst case regret is bounded by equation \ref{eqn:ucb_worst_case_regret}, see \citet{Bubeck2012}.

\eqn{
\label{eqn:ucb_worst_case_regret}
\regret \in \bigo{\sqrt{kT\log(T)}}
}

\begin{figure}
\caption{The regret bound in equation \ref{eqn:ucb_problem_dependent_regret} grows as the differences between the expected rewards for each arm shrink. The solid curve shows the mean (cummulative) regret, over a 1000 simulations for a 2-armed, bernoulli bandit with fixed horizon, $T = 500$, as a function of the difference in the expected reward for the arms $\Delta$. The dashed curves show the corresponding upper bounds; $T\Delta$ and equation \ref{eqn:ucb_problem_dependent_regret}}
\label{fig:ucb_regret_vs_delta}
\includegraphics[scale=1]{ucb_regret_vs_delta}
\end{figure}

The form of the dependence on the number of arms $k$ and horizon $T$ differs between the problem dependent and worst case regret. The problem dependent regret grows linearly with the number of arms, $k$, and logarithmically with $T$. The difference stems from the fact the problem dependent regret defines how the regret grows for a given set of reward distributions as $T$ increases, whereas in the worst case regret, the gap between expected rewards is varied as a function of $T$. \citet{Auer1995} show that the worst case regret for the k-armed bandit problem is lower bounded by,

\eqn{
\label{eqn:k-arm-bandit-lower-bound}
\regret \in \bigomega{\sqrt{kT}}
}

Subtle modifications to the UCB algorithm can eliminate the logarithmic term equation \ref{eqn:ucb_worst_case_regret}. This yeilds regret $ \bigo{\sqrt{TK}}$ and closes the gap with the worst case lower bound \cite{Audibert2009,Lattimore2015}, whilst retaining a good problem dependent bound of the form achieved by UCB \cite{Lattimore2015}.

\begin{figure}
\caption{The actual performance of the UCB algorithm can be substantially better than suggested by the upper bound, particularly for small $T$. The solid curve shows the mean expected regret associated with the sequence of arms chosen by UCB-1 with $k=2$ arms and the rewards sampled from $bernoulli([.3,.7])$ over 1000 simulations. The dashed curve shows the corresponding upper bound given by the minimum of $T\Delta_{max}$ and equation\ref{eqn:ucb_problem_dependent_regret}.}
\label{fig:ucb_upperbound_vs_actual_performance}
\includegraphics[scale=1]{upper_bound_vs_actual_average_regret}
\end{figure}

\subsection{Pure-exploration problems}
Another problem that has attracted a lot of recent attention \cite{Bubeck2009,Audibert2010,Gabillon2012,Karnin2013} within the stochastic multi-armed bandit framework is \textit{pure exploration} or \textit{best arm identification}. In this setting, the horizon $T$ represents a fixed budget for exploration after which the algorithm outputs a single best arm $i$. The performance of the algorithm is measured by the simple regret; the expected difference between the mean reward of the (truly) optimal arm and the mean reward of the arm selected by the algorithm.

\vspace{0.5cm}
\begin{definition}[Simple Regret]
\eqn{
\label{eqn:simple_regret}
\simpleregret=\mu_{i^*} - \E{\mu_{\hat i^*}}.
}
\end{definition}

The best arm identification problem arises naturally in applications where there is a testing or evaluation phase, during which regret is not incurred, followed by a commercialisation or exploitation phase. For example, many strategies might be assessed via simulation prior to one being selected and deployed. The worst case simple regret for a k-armed bandit is lower bounded by equation \ref{eqn:worst_case_simple_regret_lower_bound} (\citep{Bubeck2009}).

\eqn{
\label{eqn:worst_case_simple_regret_lower_bound}
\simpleregret \in \bigo{\sqrt{K/T}}
}

\todo{discuss the key ways in which the simple regret problem differs from cummulative regret}

Pure-exploration does not mean simply playing the arm with the widest uncertainty bounds. The goal is to be sure the arm we believe is optimal is in fact optimal at the end of the exploration period.

\subsection{Adversarial Bandits}

Adversarial bandits are an alternate, widely studied, setting that relaxes the assumption that rewards are generated stochastically. Instead, simultaneously with the learner selecting an action $a_t$, a potentially malicious adversary selects the reward vector $\boldsymbol{Y}_t$. As in the stochastic setting, the learner then receives reward only for the selected action.

\vspace{0.5cm}
\begin{definition}[Adversarial k-armed bandit problem]
Let $\actionspace = \set{1,...k}$ be the set of available actions.  In each round $t \in 1,...,T$, 
\begin{enumerate}
\item the world (or adversary) generates, but does not reveal, a vector or rewards $\vec{Y_t}=[Y_{t,1},...,Y_{t,k}]$. 
\item the learner selects an action $a_{t} \in \set{1,...,k}$, based on the actions and rewards from previous time-steps and a (potentially stochastic) \emph{policy} $\pi$
\item the learner observes and recieves (only) the reward for the selected action $Y_{t,a_t}$ 
\end{enumerate} 
\end{definition}

Adversaries that generate rewards independently of the sequence of actions selected by the learner in previous time steps are referred to as \emph{oblivous}, as opposed to \emph{non-oblivous} adversaries, which can generate rewards as a function of the history of the game. In the case of oblivous adversaries, we can also define the adversarial bandit problem by assuming the adversary generates the entire sequence of reward vectors before the game commences.

The pseudo-regret for adversarial bandits is defined, in the same way as for stochastic bandits, as the difference between the reward obtained by playing the single arm with the highest expected reward in every round and the expected reward obtained by the algorithm.

\eqn{
\label{eqn:pseudo_regret-adversarial}
\regret(\pi) &= \max_{i \in \set{1,...,k}}\E{\sum_{t=1}^T{Y_{t,i}}} - \E{\sum_{t=1}^T{Y_{t,a_t}}}
}

The policy (or algorithm) used by the learner is avaiable to the adversary before the game begins, and there are no limitations placed on the amount of computation the adversary can perform in selecting the reward sequences. This implies the adversary can ensure that any learner with a deterministic policy suffers regret $\bigo{T}$ by forecasting their entire sequence of actions. For example, if the learner will play $a_1 = 1$ in the first round, then the adversary sets the reward $\vec{Y_1} = [0,1,1,...1]$, forcasts what action the learner will play in round 2, given they recieved a reward of 0 in round 1, and again generates the reward vector such that the action the learner will select obtains no reward, and all other actions obtain the maximum reward. This implies adversarial bandit policies must be sufficiently random to avoid such exploitation \footnote{The UCB algorithm, defined by algorithm \ref{alg:ucb-1}, is deterministic if the order in which arms are played during the first $k$ rounds is fixed and the method for selecting which arm to play when multiple-arms have the same upper-confidence bound is not-random (for example, select the arm one with the lowest index $i$).}

The seminal algorithm for adversarial bandits is Exp-3 \citep{Auer2002}, which, like UCB, obtains worst case psuedo-regret of $\bigo{\sqrt{TK\log(T)}}$  \cite{Auer1995}. Optimal algorithms, with $\regret = \bigo{\sqrt{TK}}$, have also been demonstrated for the oblivious adversarial setting \cite{Audibert2009}. The focus, for adversarial bandits, is on analysing the worst case regret because the problem dependent regret is not well defined without additional assumptions. However there has been recent work on developing algorithms that are optimised for both the adversarial and stochastic settings, in that they are sufficiently cautious to avoid linear regret in the adversarial setting but can nontheless obtain good problem dependent regret in more favourable enviroments \citep{bubeck2012bothworlds,Auer2016}.

Adversarial bandits appear to be more applicable to real world problems because they do not assume that the rewards associated with each arm are constant over time or independent of the previous actions of the learner. However, psuedo-regret, as defined in equation \ref{eqn:pseudo_regret-adversarial}, is not a good measure of an algorithms performance in such cases because it is defined with respect to playing the single arm with the best average return over the game. In settings were the rewards change over time, the pseudo-regret can be negative, see figure \ref{fig:non-stationary-bandit}, so upper bounds on the psuedo-regret do not reflect how sub-optimal the algorithm may be. Adversarial bandit algorithms may perform better in non-stationary settings than standard stochastic policies to the extend that they explore more (to avoid the adversary simulating their behaviour), however it is preferable to develop algorithms specifically for non-stationary settings (subject to assumptions about how rapidly or frequently rewards can change), see for example \citep{garivier2008upper,Garivier2011a,Besbes2014}.

\begin{figure}
  \caption{The pseudo-regret can be negative if rewards are non-stationary. This example shows the results of 1000 simulations of running the UCB-1 algorithm on a 2-armed bernoulli bandit problem where the expected rewards change linearly over time, up to a horizon $T=10,000$. Figure (a) shows the expected rewards of each arm, and the proportion of time that arm-1 is played, as a function of time. The single best-arm is arm-1 as it has the highest expected reward (averaged over $t$). An oracle that selects arm-1 in every round obtains an expected reward of $5,000$. However, despite not being designed to do so, the UCB-algorithm can adapt to the changing reward distribution to obtain costistently higher rewards. The distribution of regret over the 1000 simulations is shown in figure (b).}\label{fig:non-stationary-bandit}
    \begin{subfigure}[t]{0.49\textwidth}
	\centering   
	 \caption{Behaviour over time}\label{fig:non-stationary-bandit-time} 
         \includegraphics[scale=.5]{non-stationary-bandit-time}
\end{subfigure}
    \begin{subfigure}[t]{0.49\textwidth}
    \centering
     \caption{Cummulative regret distribution}
        \label{fig:non-stationary-bandit-regret}
        \includegraphics[scale=.5]{non-stationary-bandit-regret}
    \end{subfigure}
\end{figure}

\subsection{Contextual bandits}
Contextual bandits are a generalisation of multi-armed bandits.

@@

\subsection{Markov decision processes}

@@

This is reasonable in settings where we have many similar but independent units or individuals and the goal is to identify which action is optimal (in a given context), as occurs in standard experimental settings as well.

Relation to SUTVA assumption, selecing a action for one 'unit' does not effect the reward distributions for other units.

@@

\section{Questions}
\begin{enumerate}
\item When does the expected regret make sense as the thing we actually would wish to optimise? Is optimising the expected regret any different to optimising the psuedo-regret? Who is the definition of regret down to? Does this definition of regret come from learning with expert advise?
\item Is there a reference for the doubling trick? Is it an automatic way of converting a fixed horizon algorithm to an anytime one?
\item Why is the dependence on the number of arms $K$ in the problem dependent bounds but $\sqrt{K}$ in the worst case bounds?
\item rewards in the multi-armed bandit setting can be sampled from some joint distribution?
\item Is Learning from logged feedback data just covariate shift too?
\item In contextual bandits, does it ever make sense that $Y$ causes $X$? If the reward is some function of the action taken and the context, then the full vector of counterfactual outcomes $Y$ is never instantiated. Are there any implications of this for inference?
\item Why does anything solving a regression problem work in the anti-causal direction - it would seem to break the fundamental underlying assumption of additive noise?
\item is there a benchmark library of implementations of key bandit algorithms?
\item Bubeck 2012 states that if the adversary is oblivious, the psuedo-regret coincides with the standard regret, 'which is always the ultimate quantity of interest'. Why, they are not the same for stochastic bandits are they?
\item what is the worst-case regret of UCB in an adversarial setting?
\item is there a concept of problem dependent regret for adversarial bandits? Has there been analysis of the problem dependent regret for key adversarial algorithms such as EXP-3?
\item adversarial regret bounds for Thompson sampling, UCB with random arm selection from upper-bound set?
\item do continuous armed bandits implie that there are arms with any arbitrary gap in reward (including worst case gap for that T) and thus you always end up with something like worst case regret?)
\item in what real world setting do adversarial bandits potentially make sense?
\end{enumerate}
